p-CAPTCHAs and the Recognition Problem

### 2012-02-15 frostedglass/paper.tex
Changed the way the images were displayed. (It still isn't looking right though.)

\documentclass[12pt]{article}
%\usepackage{grapicx}
\usepackage{subfig}
\usepackage{float}
\floatstyle{boxed}
\restylefigure{float}

\begin{document}
\begin{center}p-CAPTCHAs and the Recognition Problem\end{center}

@@

\begin{figure}
	\centering	
	\subfloat{\label{fig:plainSK}\includegraphics[width=.25]{plainSK.bmp}}
	\subfloat{\label{fig:frostySK}\includegraphics[width=.25]{frostySK.bmp}}
	\subfloat{\label{fig:SKbreaklines}\includegraphics[width=.25]{SKbreaklines.bmp}}
	\subfloat{\label{fig:SK435239}\includegraphics[width=.25]{SK435239.bmp}}
	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
	\label{fig:EncryptionProcess}
\end{figure}

@@

	The image above was encrypted by permuting 48 blocks. Although there are 48-factorial permutations of 48 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

@@

\begin{figure}
	\centering	
	\subfloat{\label{fig:SK435240}\includegraphics[width=.25]{SK435240.bmp}}
	\subfloat{\label{fig:SK435241}\includegraphics[width=.25]{SK435241.bmp}}
	\subfloat{\label{fig:SK435242}\includegraphics[width=.25]{SK435242.bmp}}
	\subfloat{\label{fig:SK435243}\includegraphics[width=.25]{SK435243.bmp}}
	\caption{Can your computer recognize the true plaintext?}
	\label{fig:RecognitionProblem}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefigure{float}

\begin{document}
\title{p-CAPTCHAs and the Recognition Problem}
\author{Ben Warner}
\maketitle

@@

\begin{figure}
	\includegraphics[scale=.5]{warpedSK.png}
	\includegraphics[scale=.5]{warpedfrosty.png}
	\includegraphics[scale=.5]{SKBreakLines.jpg}
	\includegraphics[scale=.5]{SK75391.png}
	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
\label{warpedSK}
\end{figure}

%\begin{figure}
%	\centering	
%	\subfloat{\label{fig:warpedSK}\includegraphics[width=.25]{warpedSK.png}}
%	\subfloat{\label{fig:warpedfrosty}\includegraphics[width=.25]{warpedfrosty.png}}
%	\subfloat{\label{fig:SKbreaklines}\includegraphics[width=.25]{SKbreaklines.png}}
%	\subfloat{\label{fig:SK75391}\includegraphics[width=.25]{SK75391.png}}
%	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
%	\label{fig:EncryptionProcess}
%\end{figure}

@@

	The image above was encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

@@

\begin{figure}
	\includegraphics[scale=.5]{SK75392.png}
	\includegraphics[scale=.5]{SK75393.png}
	\includegraphics[scale=.5]{warpedfrosty.png}
	\includegraphics[scale=.5]{SK75395.png}
	\caption{Can your computer recognize the true plaintext?}
\label{warpedSK}
\end{figure}

%\begin{figure}
%	\centering
%	\subfloat{\label{fig:SK75393}\includegraphics[width=.25]{SK75393.png}}
%	\subfloat{\label{fig:SK75392}\includegraphics[width=.25]{SK75392.png}}
%	\subfloat{\label{fig:warpedfrosty}\includegraphics[width=.25]{warpedfrosty.png}}
%	\subfloat{\label{fig:SK75394}\includegraphics[width=.25]{SK75394.png}}
%	\caption{Can your computer recognize the true plaintext?}
%	\label{fig:RecognitionProblem}
%\end{figure}
